---
title: "RADseq Stacks"
subtitle: "Mouse GBS using Stacks"
author: "Lucas A. Nell"
date: "June 8, 2016"
output:
  html_document:
    highlight: haddock
    theme: default
  pdf_document:
    highlight: haddock
    latex_engine: xelatex
geometry: margin=1in
fontsize: 12pt
mainfont: Helvetica
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```


# Initial steps

It's assumed that all steps from `RADseq_base.Rmd` have been carried out.


# Stacking

## Create stacks

First we had to create stacks from the aligned BAM files using Stacks' `pstacks`. Because
BAM names included a unique integer after the first underscore, I used that for the id.

> Stacks doesn't appear to be very efficient at running multithreaded jobs, so I 
> recommend using something like Python's `multiprocessing` module to run `pstacks` on
> multiple files at once.

```{r pstack, engine = 'bash'}
cd /path/to/bam
export numThreads=12
export outPath=/path/to/stacks/

for bam in *.bam
do
    tmp=(`echo ${bam/%.bam/} | tr '_' ' '`)
    id=${tmp[1]}
    /usr/local/apps/stacks/latest/bin/pstacks -t bam \
        -f ${bam} \
        -o ${outPath} \
        -i ${id} \
        -p ${numThreads} &> ./logs/pstacks_${id}.log
done
```

## Create stack catalog

Creating catalog using `cstacks`.

```{r cstack, engine = 'bash'}
cd /path/to/stacks
export numThreads=12
export outPath=./catalog/

pStacks=(`ls *.tags.tsv.gz | sed 's/.tags.tsv.gz//g'`)
export pStacks=${pStacks[@]/#/' -s '}

/usr/local/apps/stacks/latest/bin/cstacks \
    -b 1 \
    ${pStacks} \
    -o ${outPath} \
    -p ${numThreads} &> ${outPath}/catalog.log
```



## Search all samples against catalog

Search all samples from the `pstacks` step against catalog, using `sstacks`.

```{r sstack, engine = 'bash'}
cd /path/to/stacks
export numThreads=12
export outPath=./sets/
export catalogFile=./catalog/batch_1

pStacks=(`ls *.tags.tsv.gz | sed 's/.tags.tsv.gz//g'`)
export pStacks=${pStacks[@]/#/' -s '}

/usr/local/apps/stacks/latest/bin/sstacks \
    -b 1 \
    -c ${catalogFile} \
    ${pStacks} \
    -o ${outPath} \
    -p ${numThreads} &> ${outPath}/search.log
```


